A Global Picture of Food Insecurity and Hunger

### 2020-09-19 docs/modeling_fies.tex
final final lol

\subsection{Covariates}
We model subnational rates of severe and moderate-to-severe food insecurity as a function of several covariates related to human development, food security, health, infrastructure, and the environment (See Table \ref{tab:covars}).  We aimed for covariates that had subnational spatial resolution and peer-reviewed projections available through the year 2030.  For many variables, we combined historic subnational data with national projections through the 2020s to derive simple subnational estimates for the next decade.  For projections based on the Shared Socioeconomic Pathways (SSP) framework, we used the middle-of-the-road pathway, SSP2, and for climatological variables, we use forecasts based on Representative Concentration Pathway (RCP) 6.0.  Finally, we adjusted several variables to account for the effects of COVID-19, including GDP per capita using June 2020 estimates from the World Bank \citep{prospects2020}, stunting and wasting using August 2020 estimates published in \textit{The Lancet} \citep{headey2020impacts}, as well as the poverty headcount index \cite{cuaresma2018will}.  For a detailed overview of the steps involved in processing and preparing each covariate, see the Appendix.

@@

\subsection{Poverty Headcount Index}
We used estimates of the Poverty Headcount Index for the recent past and future from the World Poverty Clock by the World Data Lab \citep{cuaresma2018will}, updated to include the impact of the coronavirus. In our model we include national level poverty rates at a threshold of \$1.90 which is defined as \textit{extreme} poverty. By using the concept of parameterized Lorenz curves in combination with mean income/consumption and population projections future poverty rates are calculated. For more details on the methodology and information on global and country level poverty check the website \url{worldpoverty.io}.

>>>>

\subsection{Covariates}
We model subnational rates of severe and moderate-to-severe food insecurity as a function of several covariates related to human development, food security, health, infrastructure, and the environment (See Table \ref{tab:covars}).  We aimed for covariates that had subnational spatial resolution and peer-reviewed projections available through the year 2030.  For many variables, we combined historic subnational data with national projections through the 2020s to derive simple subnational estimates for the next decade.  For projections based on the Shared Socioeconomic Pathways (SSP) framework, we used the middle-of-the-road pathway, SSP2, and for climatological variables, we use forecasts based on Representative Concentration Pathway (RCP) 6.0.  Finally, we adjusted several variables to account for the effects of COVID-19, including GDP per capita using June 2020 estimates from the World Bank \citep{prospects2020}, stunting and wasting using August 2020 estimates published in \textit{The Lancet} \citep{headey2020impacts}, as well as the poverty headcount index \cite{Cuaresma2018}.  For a detailed overview of the steps involved in processing and preparing each covariate, see the Appendix.

@@

\subsection{Poverty Headcount Index}
We used estimates of the Poverty Headcount Index for the recent past and future from the World Poverty Clock by the World Data Lab \citep{Cuaresma2018}, updated to include the impact of the coronavirus. In our model we include national level poverty rates at a threshold of \$1.90 which is defined as \textit{extreme} poverty. By using the concept of parameterized Lorenz curves in combination with mean income/consumption and population projections future poverty rates are calculated. For more details on the methodology and information on global and country level poverty check the website \url{worldpoverty.io}.
